Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-22 lloveras_2020.tex
figuras retocadas con inkscape añadidas

{
A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona. In previous works, DEMT has been combined with a potential field source surface (PFSS) model such as \citet{huang_2012}, \citet{nuevo_2013} and \citet{nuevo_2015}. Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamic of the last two solar minima along magnetic field lines and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona throgh PFSS magnetic lines.}

{The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) is a three-dimensional (3D) physics-based, data-driven model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014} and is constantly validated with observations as new improvements are implemented. DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona. More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.
We used AWSoM results with two purposes. On the one hand to provide thermodynamic results to be contrasted with DEMT, and on the other hand to provide magnetohydrodynamic (MHD) coronal magnetic field model that is used to study thermodynamics along field lines.
}

We carry out a quantitatively detailed comparative {DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24. To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B \citep{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used {for DEMT, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM}, while data taken by the \textit{Atmospheric Imaging Assembly instrument} {(AIA \citep{lemen_2012})}, on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208 {for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.

{
Section \ref{demt} and \ref{awsom} summarizes DEMT technique, AWSoM model, instruments, and datasets we used. Section \ref{trace} explains the technique that is used to trace the thermodynamic results along the field lines. Section \ref{energia} details the energy model and the loop integrated quantities that are part of the comparative analysis. In Section \ref{demt_res} the quantitative comparative analysis of both rotations using DEMT is described and in Section \ref{awsom_res} AWSoM results are related to the one of DEMT. Finally in Section \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.
}
\\
%{El parrafo de abajo lo pondria en la seccion 2.1}\\
%In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions. The cadence of the data time-series is set to 6\,hr. The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it.

@@

{We carried out the 3D DEMT reconstruction and MHD modeling of two target Carrington rotations (CR). We selected CR-2082 (2009, 05 April through 03 May), a deep minimum rotation between solar cycles (SC) 23 and 24, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24. To study CR-2082 and CR-2208 data taken by the STEREO/EUVI-B and SDO/AIA instruments was used, respectively. The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package. For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.}

@@

{The solution of the tomographic problem involves a very large sparse matrix. Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through \emph{regularization} techniques \citep{frazin_2000}. In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude. Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives. In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions. As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}
{The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction (covering the height range $1.0-1.25\,\mrsun$) and 2\deg\ in both the latitudinal and longitudinal directions. }

@@

AWSoM addresses coronal heating by including the non-linear interaction of forward propagating and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
The model accounts for anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature. The dissipated turbulent energy is distributed over these three temperatures based on the theories of linear wave damping and stochastic heating. AWSoM does not use ad-hoc heating functions and accounts for both collisional and collision-less electron heat conduction. The Alfv\'{e}n wave number associated with the damping rate is determined by the critical balance condition which uses the cascade time of the minor wave \citep{Lit2007} instead of the previously used cascade time of the major wave \citep{Cha2011, Van2014}. This energy partitioning, in the improved version of AWSoM, leads to more electron heating and less solar wind acceleration.% \diego{falta cita}%\citep{Van2019b}.
To solve anisotropic MHD equations with radiative cooling, heat conduction and wave turbulence, AWSoM uses the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme. MHD equations employed within the AWSoM model are detailed in \citet{Van2014}. Recently, \citet{sachdeva_2019} validated the AWSoM simulation results with a suite of observations from near the Sun upto 1 AU for solar minimum conditions.

@@

{For analysis purposes, {the traced magnetic field lines are classified as open or closed according to their full geometry. Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being {respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e. their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).}

@@

{Consider} a simple energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power($E_h$) \citep{aschwanden_2004}:

@@

{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, i.e. $E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transversal area of the magnetic flux tube at position $s$. Under a quiescent solar corona plasma regime, the conductive flux is assumed to be dominated by the electron thermal conduction, described by the usual Spitzer model \citep{spitzer_1962}

@@

{Both target rotations are highly axisymmetric, i.e. characterized by a high azymuthal symmetry. Rotation CR-2082} showed two {small} active regions (ARs), both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}. {Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}

@@

Figure 1 shows the ADAPT-GONG and GONG global
maps for CR2208. The two maps show significant dif-
ferences, especially in the polar regions. We find that
using ADAPT-GONG maps as input to the AWSoM
model produces significantly better results in compar-
ison to using GONG maps. Therefore, in this work
we use ADAPT-GONG global magnetic maps for both
CR2208 and CR

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1105.eps}
\caption{Longitude-averaged latitudinal dependence of the electron density (top) and temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$. The left (right) panels correspond to CR-2082 (CR-2208). The vertical black line indicates the longitude-averaged latitudes of the open/closed magnetic boundary in both hemispheres.}
\label{perf_lat}
\end{center}
\end{figure}

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
CR-2082\\
I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&10\%) \\
II   & 0&99 &(\Mi&25\%)  &   9&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
III  & 0&66 &(\Mi&17\%)  &   7&0 &(\Mi&~9\%) &   0&97 &(\Mi&~9\%) \\
\hline          
CR-2208\\
I    & 1&03 &(\Pl&~6\%)  &   9&7 &(\Mi&~8\%) &   1&55 &(\Mi&17\%) \\
II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
III  & 0&58 &(\Mi&~3\%)  &   8&9 &(\Mi&18\%) &   1&14 &(\Mi&18\%) \\
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of leg defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
\label{tabla_comp}
\end{table}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).} %\notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height. I believe it is interesting to compare these two curves with Figure 10. Note that while in this Figure all latitudes are magnetically open, in Figure 10 only the part at latitudes larger than the vertical black lines are open. Note that DEMT shows that in the open low corona $N_e$ decreases from the O/C boundary towards the poles, anti-correlating with the AWSoM terminal speed, which is nice. In order to quantify this anti-correlation we need to trace the terminal speed and the DEMT $N_e$, which we may need to do with the help of Chip and Nishtha. Chip, we can discuss this idea over Skype after Xmas if you are around.}
}
\label{perf_lon_vr}
\end{center}
\end{figure}

@@

In comparing the DEMT results obtained for the two selected targets, {we highlight here that} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently. They found that while the density {products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e. $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$. Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterized by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region. As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region. These systematic differences are {around or beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} {estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$}.}

@@

Results of the AWSoM model are compared to those of the DEMT reconstructions in the range of coronal heights $\approx 1.05-1.20\,\mrsun$ simultaneously covered by both models. In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines. The detailed comparison shown in this work can be summarized as follows. For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$. {The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models is considerably better than that reported in previous works. \citet{oran_2015} and \citet{jin_2012} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
\diego{Note by Diego: Chip, Nishtha, if you think we can relate some differences or observed trends of AWSoM with the magnetic field, this could be a good place, but I need your insight here.}

>>>>

A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona. In previous works, DEMT has been combined with a potential field source surface (PFSS) model  (\citet{huang_2012}, \citet{nuevo_2013}). Recently, \citet{lloveras_2017} combined DEMT with PFSS to study the thermodynamic of the last two solar minima along magnetic field lines and selecting different magnetic structures and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona throgh PFSS magnetic lines. In this article, for first time, we combined the DEMT reconstruction with the magnetic field of a MHD model, as explained in the next paragraph.

{The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) \diego{within the Space Weather Modeling Framework (SWMF)} is a three-dimensional (3D) physics-based, data-driven model extending from the upper chromosphere, into the solar corona upto 1 AU (and beyond) \citep{vander_2010, Van2014} and is constantly validated with observations as new improvements are implemented. DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona. More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.
We used AWSoM results with two purposes. On the one hand to provide thermodynamic results to be contrasted with DEMT, and on the other hand to provide magnetohydrodynamic (MHD) coronal magnetic field model that is used to study thermodynamics along field lines.
}

We carry out a quantitatively detailed comparative {DEMT/AWSoM} analysis of the Carrington Rotation (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum and CR-2208 (2018, 02 September through 29 September) during the declining fase of SC 24. To study CR-2082 with DEMT technique, data taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) were used, and Global Oscillation Network Group (GONG) magnetogram as the only input for AWSoM, while data taken by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} (SDO) mission were used to study CR-2208 {for DEMT, and Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG magnetograms for AWSoM}.

%We carry out a quantitatively detailed comparative DEMT/AWSoM analysis of the Carrington Rotation (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum and CR-2208 (2018, 02 September through 29 September) during the declining fase of SC 24. To study CR-2082 with DEMT technique data taken by the Extreme UltraViolet Imager Behind (EUVI-B (Wuelser et al.,2004)) on board the Solar TErrestrial RElations Observatory (STEREO) was used, while data taken by the Atmospheric Imaging Assembly instrument (AIA (Lemen et al., 2012)), on board the Solar Dynamics Observatory (SDO) mission was used to study. Global Oscillation Network Group (GONG) synoptic magnetogram was used as the only input for AWSoM model to the same two target rotations. In the case of CR-2208 Air Force Data Assimilation Photosph eric flux Transport (ADAPT)-GONG magnetogram map was used as input of the model.

Section \ref{demt} and \ref{awsom} summarizes DEMT technique, and  AWSoM model respectively. Section \ref{trace} explains the method that is used to trace the thermodynamic results along the field lines of the magnetic model. Section \ref{energia} details the energy model and the loop integrated quantities. In Section \ref{demt_res} the quantitative comparative analysis of both rotations using DEMT is described and in Section \ref{awsom_res} AWSoM results are related to the one of DEMT. Finally in Section \ref{discu} summarizes and discusses the main conclusions of this analysis, and anticipates further planned work.

%{El parrafo de abajo lo pondria en la seccion 2.1}\\
%In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions. The cadence of the data time-series is set to 6\,hr. The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it.

@@

{We carried out the 3D DEMT reconstruction of two target Carrington rotations (CR). We selected CR-2082, a deep minimum rotation between solar cycles (SC) 23 and 24, and CR-2208, a rotation during the early declining fase of SC 24. To study CR-2082 and CR-2208 data taken by the STEREO/EUVI-B and SDO/AIA instruments was used, respectively. The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package. For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.}

@@

{The solution of the tomographic problem involves a very large sparse matrix. Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}. In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude. Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives. In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions. As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}
{The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction (covering the height range $1.0-1.25\,\mrsun$) and 2\deg\ in both the latitudinal and longitudinal directions. }

@@

We perform a MHD modeling of the two target rotations studied with DEMT. For this propose we use the MHD coronal model AWSOM which addresses coronal heating by including the non-linear interaction of forward propagating and counter-propagating (reflected) Alfv\'{e}n waves which results in a turbulent cascade.
The model accounts for anisotropic (parallel and perpendicular) proton temperatures and isotropic electron temperature. The dissipated turbulent energy is distributed over these three temperatures based on the theories of linear wave damping and stochastic heating. AWSoM does not use ad-hoc heating functions and accounts for both collisional and collision-less electron heat conduction. The Alfv\'{e}n wave number associated with the damping rate is determined by the critical balance condition which uses the cascade time of the minor wave \citep{Lit2007} instead of the previously used cascade time of the major wave \citep{Cha2011, Van2014}. This energy partitioning, in the improved version of AWSoM, leads to more electron heating and less solar wind acceleration.% \diego{falta cita}%\citep{Van2019b}.
To solve anisotropic MHD equations with radiative cooling, heat conduction and wave turbulence, AWSoM uses the Block-Adaptive-Tree-Solarwind-Roe-Upwind Scheme (BATS-R-US, \citealp{Pow1999, Tot2012}) numerical scheme. MHD equations employed within the AWSoM model are detailed in \citet{Van2014}. Recently, \citet{sachdeva_2019} validated the AWSoM simulation results with a suite of observations from near the Sun upto 1 AU for solar minimum conditions.

@@

{For analysis purposes, {the traced magnetic field lines are classified as open or closed according to their full geometry. Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being {respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (\textit{i.e.} their location at $r=1\,\mrsun$) to its apex (\textit{i.e.}, the location of maximum height).}

@@

{Consider} a simple energy balance for each magnetic flux tube, {in which the dominating losses of} radiative power ($E_r$) and thermal conduction power ($E_c$) are compensated {by a} coronal heating power ($E_h$) \citep{aschwanden_2004}:

@@

{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, \textit{i.e.} $E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transversal area of the magnetic flux tube at position $s$. Under a quiescent solar corona plasma regime, the conductive flux is assumed to be dominated by the electron thermal conduction, described by the usual Spitzer model \citep{spitzer_1962}

@@

{Both target rotations are highly axisymmetric, \textit{i.e.} characterized by a high azymuthal symmetry. Rotation CR-2082} showed two {small} active regions (ARs), both near latitude $+30\mdeg$ and {around longitudes} $50\mdeg$ and $120\mdeg${, respectively}. {Rotation CR-2208} showed two {ARs, both near latitude} $+5\mdeg$ and {around longitudes $140\mdeg$ and $300\mdeg$, respectively.}

@@

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1105_2.pdf}
\caption{Longitude-averaged latitudinal dependence of the electron density (top), temperature (mid) and $Br$ for CR-2082 (blue) and CR-2208 (red) results at $1.105\,\mrsun$. Dashed lines correspond to AWSoM results while solid line to DEMT. The vertical black line indicates the longitude-averaged latitudes of the open/closed magnetic boundary in both hemispheres.}
\label{perf_lat}
\end{center}
\end{figure}

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
CR-2082\\
I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&10\%) \\
II   & 0&99 &(\Mi&25\%)  &   9&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
III  & 0&66 &(\Mi&17\%)  &   7&0 &(\Mi&~9\%) &   0&97 &(\Mi&~9\%) \\
\hline          
CR-2208\\
I    & 1&03 &(\Pl&~6\%)  &   9&7 &(\Mi&~8\%) &   1&55 &(\Mi&17\%) \\
II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
III  & 0&58 &(\Mi&~3\%)  &   8&9 &(\Mi&18\%) &   1&14 &(\Mi&18\%) \\
\hline   
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of leg defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
\label{tabla_comp}
\end{table}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995_2.pdf}
\caption{{Longitude-averaged latitudinal dependence of the AWSoM model wind speed at $6.0\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).} %\notebyalbert{(by Albert): Even if this is not yet the terminal speed, it is a pretty high height, and one can already see the transition from FAST to SLOW speed in the model, where the absolute minimum indicates the location of the HCS at this height. I believe it is interesting to compare these two curves with Figure 10. Note that while in this Figure all latitudes are magnetically open, in Figure 10 only the part at latitudes larger than the vertical black lines are open. Note that DEMT shows that in the open low corona $N_e$ decreases from the O/C boundary towards the poles, anti-correlating with the AWSoM terminal speed, which is nice. In order to quantify this anti-correlation we need to trace the terminal speed and the DEMT $N_e$, which we may need to do with the help of Chip and Nishtha. Chip, we can discuss this idea over Skype after Xmas if you are around.}
}
\label{perf_lon_vr}
\end{center}
\end{figure}

@@

In comparing the DEMT results obtained for the two selected targets, {we highlight here that} they rely on data provided by two different instruments, {namely EUVI and AIA for CR-2082 and CR-2208, respectively.} In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently. They found that while the density {products are} essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, \textit{i.e.} $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$. Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was {characterized by temperatures $\approx 10-15\%$ larger relative to CR-2082} throughout the streamer belt region. As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region. These systematic differences are {around or beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} {estimated to be $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$}.}

%\diego{As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region. The uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), was estimated {at $\Delta\Tm\approx 10\%$ and $\Delta\sqravgN\approx 5\%$ by \citet{lloveras_2017}}. Considering uncertainty levels CR-2208 is characterized by slightly larger temperatures and definitely lower densities.}

@@

Results of the AWSoM model are compared to those of the DEMT reconstructions in the range of coronal heights $\approx 1.05-1.20\,\mrsun$ simultaneously covered by both models. In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines. The detailed comparison shown in this work can be summarized as follows. For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$. {The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both target rotations{, with larger discrepancies in the CHs.} This level of agreement between both models \diego{(within or slightly above the uncertainty)} is considerably better than that reported in previous works. \citet{jin_2012} and \citet{oran_2015} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.} \notebyalbert{Chip, if Section 2.2 explains the most significant improvements of AWSoM since the version used in those references, we can comment on the reason for the improvement here.}
\diego{Note by Diego: Chip, Nishtha, if you think we can relate some differences or observed trends of AWSoM with the magnetic field, this could be a good place, but I need your insight here.}
